---
title: "Solution Of Exercices"
author: "SAMO Marius"
date: '2022-06-22'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# CHAPTER 2 : R Basics

## EXERCICE 1 : The very basics

$$1+2+3+...+n=\frac{n(n+1)}{2}$$

### QUESTION 1

```{r}
 
n <- 100
sum_integers_1 <- (n*(n+1))/2
sum_integers_1


```

### QUESTION 2

```{r}
n <- 1000
sum_integers <- (n*(n+1))/2
sum_integers

```

### QUESTION 3

**answer** : **seq** creates a list of numbers and **sum** adds them up.

```{r}
n <- 1000
x <- seq(1, n)
sum(x)
```

### QUESTION 4

```{r}

log10(sqrt(100))

```

### QUESTION 5

**answer** : $log(exp(x)) = x$

## EXERCICE 2 : Data types

### QUESTION 1

**answer** : The state name, the abbreviation of the state name, the state's region, and the state's population and total number of murders for 2010.

```{r}
library(dslabs)
data(murders)
str(murders)
```

### QUESTION 2

```{r}
names(murders)
```

### QUESTION 3

```{r}
a <- murders$state
class(a)
```

### QUESTION 4

```{r}
b <- murders["state"]
identical(a,b)
```

### QUESTION 5

```{r}
length(levels(murders$region))
```

### QUESTION 6

```{r}
table(murders$region)
```

## EXERCICE 3 : Vectors-Coercion

### QUESTION 1

```{r}
temp <- c(35, 88, 42, 84, 81, 30)
temp
```

### QUESTION 2

```{r}
city <- c("Beijing", "Lagos", "Paris", "Rio de Janeiro", "San Juan", "Toronto")
city
```

### QUESTION 3

```{r}
names(temp) <- city
temp
```

### QUESTION 4

```{r}

temp[1:3]

```

### QUESTION 5

```{r}
temp[c("Paris", "San Juan")]

```

### QUESTION 6

```{r}
12:73
```

### QUESTION 7

```{r}
seq(1,100,2)
```

### QUESTION 8

```{r}
seq(6,55,4/7)

length(seq(6,55,4/7))
```

### QUESTION 9

```{r}
a <- seq(1, 10, 0.5)
class(a)
```

### QUESTION 10

```{r}
a <- seq(1,10)
class(a)
```

### QUESTION 11

```{r}
x <- c("1", "3", "5")
x <- as.numeric(x)
x
```

## EXERCICE 4 : Sorting

### QUESTION 1

```{r}
pop <- murders$population
pop <- sort(pop)
pop[1:3]
```

### QUESTION 2

```{r}
order(murders$population)[1]
```

### QUESTION 3

```{r}
which.min(murders$population)
```

### QUESTION 4

```{r}
states <- murders$state
states[51]
```

### QUESTION 5

```{r}
rank <- rank(murders$population)
my_df <- data.frame(states, rank)
my_df
```

### QUESTION 6

```{r}
ind <- order(murders$population)
my_df$states <- my_df$states[ind]
my_df$rank <- my_df$rank[ind]
my_df
```

### QUESTION 7

```{r}
data("na_example")
str(na_example)

sum(is.na(na_example))
```

### QUESTION 8

```{r}
mean(na_example, na.rm = TRUE)
```

## EXERCICE 5 : Vectors arithmetics

### QUESTION 1

```{r}
temp <- c(35, 88, 42, 84, 81, 30)
city <- c("Beijing", "Lagos", "Paris", "Rio de Janeiro", 
          "San Juan", "Toronto")
city_temps <- data.frame(name = city, temperature = temp)

city_temps["temperature_C"] = (city_temps$temperature-32)*(5/9)
city_temps
```

### QUESTION 2

$$ 1+\frac{1}{2^2}+\frac{1}{3^2}+...+\frac{1}{100^2} \approx  \frac{\pi^2}{6} $$

```{r}

sum(1/(seq(1,100)^2))

```

### QUESTION 3

```{r}

murder_rate <- murders$total*100000/murders$population
mean(murder_rate)

```

## EXERCICE 6 : Indexing

### QUESTION 1

```{r}
murder_rate <- murders$total*100000/murders$population
low <- murder_rate < 1
low
```

### QUESTION 2

```{r}
ind <- which(low)
ind
```

### QUESTION 3

```{r}

murders$state[ind]

```

### QUESTION 4

```{r}
low <- low &  murders$region == "Northeast"
murders$state[which(low)]

```

### QUESTION 5

```{r}

sum(length(murder_rate < mean(murder_rate)))

```

### QUESTION 6

```{r}

ind <- match(c("AK", "MI", "IA"), murders$abb)

murders$state[ind]
```

### QUESTION 7

```{r}

abb <- c("MA","ME", "MI", "MO", "MU")

abb[abb %in% murders$abb]

```

### QUESTION 8

```{r}
abb[ !(abb %in% murders$abb)]

```

## EXERCICE 7 : Plot

### QUESTION 1

```{r}
population_in_millions <- log10(murders$population/10^6)
total_gun_murders <- log10(murders$total)

plot(population_in_millions, total_gun_murders)


```

### QUESTION 2

```{r}

with(murders, hist(population))
```

### QUESTION 3

```{r}
with(murders, boxplot(population ~ region))
```
