---
title: "GGPLOT"
author: "SAMO KAMGA MARIUS BARTEL"
date: "01/08/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## EXERCICE 1

### QUESTION 1

```{r}
library(dplyr)
library(ggplot2)
library(dslabs)
data(heights)
data(murders)
```


```{r}
p <- murders %>% ggplot()
class(p)
```
### QUESTION 2

**answer** : b-) A blank slate plot

```{r}
print(p)
```



### QUESTION 3


```{r}
p <- heights %>%
  ggplot()
```


### QUESTION 4

```{r}
class(p)
```


### QUESTION 5

**answer** : c-) total and population

### QUESTION 6

```{r}

murders %>% ggplot(aes(x = population, y = total)) +
  geom_point()

```
### QUESTION 7

```{r}
murders %>% ggplot(aes(total, population)) +
  geom_point()
```


### QUESTION 8

**answer** : a-) We need to map a character to each point through the label argument in aes.


### QUESTION 9

```{r}
murders %>% ggplot(aes(population, total)) + geom_label(aes(label = abb))


```


### QUESTION 10

**answer** : d-) Because we want all colors to be blue, we do not need to map colors, just use the color argument in geom_label.

### QUESTION 11

```{r}

murders %>% ggplot(aes(population, total)) + geom_label(aes(label = abb), color = "blue")
```

### QUESTION 12

**answer** : b-) Because each label needs a different color we map the colors through the color argument of aes .

### QUESTION 13

```{r}
murders %>% ggplot(aes(population, total)) + geom_label(aes(label = abb, color = region))
```

### QUESTION 14

```{r}
p <- murders %>% 
  ggplot(aes(population, total, label = abb, color = region)) +
  geom_label() 

p + scale_x_log10()
```


### QUESTION 15

```{r}
p <- murders %>% 
  ggplot(aes(population, total, label = abb, color = region)) +
  geom_label() 

p <- p + scale_x_log10() + scale_y_log10()

p
```

### QUESTION 16

```{r}
p + ggtitle(label = "Gun murder data")

```

















