---
title: "Solutions_chapter4"
author: "SAMO KAMGA MARIUS BARTEL"
date: "27/06/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## EXERCICE 1 : Tidy data

### QUESTION 1

```{r}

```

### QUESTION 2

**answer** : a-) ChickWeight is not tidy: each chick has more than one row.

```{r}
length(unique(ChickWeight$weight)) == nrow(ChickWeight)

```
### QUESTION 3

**answer** : c-) BOD is tidy: each row is an observation with two values (time and demand)

### QUESTION 4

**answer** : Formaldehyde, 


## EXERCICE 2 : Manipulating data frames

### QUESTION 1


```{r}
library(dplyr)
library(dslabs)
data(murders)

```


```{r}

murders <- mutate(murders, rate = total / population * 100000)

```


### QUESTION 2


```{r}
murders <- mutate(murders, rank = rank(-rate))
```


### QUESTION 3

```{r}

select(murders, state, abb) %>% head()
```

### QUESTION 4

```{r}
filter(murders, rank %in% 1:5) %>% head()
```


### QUESTION 5

```{r}

no_south <- filter(murders, region != "South")
nrow(no_south)
```

### QUESTION 6


```{r}

murders_nw <- filter(murders, region %in% c("Northeast", "West"))

head(murders_nw)
```



### QUESTION 7

```{r}

my_states <- filter(murders,  region %in% c("Northeast", "West"), rate <1 ) 
select(my_states, state, rate, rank)

```


## EXERCICE 3 : The pipe

### QUESTION 1


```{r}

 murders %>%
  mutate(rate =  total / population * 100000, 
                  rank = rank(-rate)) %>%
  filter(region %in% c("Northeast", "West"), 
                      rate < 1) %>%
  select(state, rate, rank)


```


### QUESTION 2


```{r}
data("murders")
my_states <- murders %>%
  mutate(rate =  total / population * 100000, 
                  rank = rank(-rate)) %>%
  filter(region %in% c("Northeast", "West"), 
                      rate < 1) %>%
  select(state, rate, rank)

my_states %>% head()
```


## EXERCICE 3 : Manipulating data frames

```{r}
library(NHANES)
data(NHANES)
```

### QUESTION 1

```{r}

ref <- NHANES %>%
  filter(AgeDecade == " 20-29") %>%
  summarise(average = mean(BPSysAve, na.rm = TRUE), sd = sd(BPSysAve, na.rm = TRUE))

ref
```

### QUESTION 2

```{r}
ref_avg <- ref %>%
  pull(average)

ref_avg
```

### QUESTION 3

```{r}
NHANES %>%
  filter(AgeDecade == " 20-29") %>%
  summarise(min = min(BPSysAve, na.rm = TRUE), max = max(BPSysAve, na.rm = TRUE))
```

### QUESTION 4

```{r}
NHANES %>%
  filter(Gender == "female") %>%
  group_by(AgeDecade) %>%
  summarise(average = mean(BPSysAve, na.rm = TRUE), sd = sd(BPSysAve, na.rm = TRUE))
```

### QUESTION 5

```{r}
NHANES %>%
  filter(Gender == "male") %>%
  group_by(AgeDecade) %>%
  summarise(average = mean(BPSysAve, na.rm = TRUE), sd = sd(BPSysAve, na.rm = TRUE))
```

### QUESTION 6

```{r}

NHANES %>%
  group_by(AgeDecade, Gender) %>%
  summarise(average = mean(BPSysAve, na.rm = TRUE), sd = sd(BPSysAve, na.rm = TRUE))

```

### QUESTION 7

```{r}
NHANES %>%
  filter(AgeDecade == " 40-49") %>%
  group_by(Race1) %>%
  summarise(average = mean(BPSysAve, na.rm = TRUE)) %>%
    arrange(average)
```



























































